{\itshape Advanced Robotics} A simple path optimization method for motion planning

### 2015-10-13 paper.tex
Add FIAD figures, correct mistakes

\jvol{00} \jnum{00} \jyear{2013} \jmonth{January}

@@

For this shortening purpose, random shortcut (RS) methods are
still very popular~\cite{Sekhavat-Svestka1998,HauserFastSmooth}. However, RS requires fine tuning of the termination condition (see 
Algorithm~\ref{algo:random-shortcut}) and is no efficient due to randomness for long 
trajectories where only a small part needs to be optimized. 
Figure~\ref{decoupled_DOF_optimization} presents another situation where RS will 
always fail to optimize the initial path, since it cannot decouple the 
robot degrees of freedom (DOF) on which the optimization occurs, contrary to our 
algorithm or partial random shortcut (PRS) methods~\cite{Geraerts04clearancebased} that shortcut only one or a group of DOF.

@@

The idea of our method is to find a good trade-off between
the simplicity of “blind” methods like shortcut algorithm,
and the complexity of distance based optimization techniques.
The method iteratively shortens the initial path with gradient-based information.
When a collision is detected at a given iteration, the method backtracks to the
latest valid iteration and inserts a linearized transformation constraint
between the objects detected in collision. Only few distances between objects are evaluated, therefore no pre-processing of the
robot or environment models is necessary. The underlying optimization
algorithm is a quadratic program.

@@

Some heuristics use random shortcuts on the initial guess combined with a 
trajectory re-building that returns ${C}^1$ shortcuts made of parabolas and lines 
(bang-bang control)~\cite{HauserFastSmooth}. These local refined trajectories 
are time-optimal since they comply with acceleration and velocity constraints. 
~\cite{Guernane2011}, also based on random shooting, is guiding configuration-
generation with local holonimic considerations. But this method remains only locally 
optimal, and is not addressing high-DOF problems.
~\cite{Geraerts04clearancebased}, whereas just implemented for freeflyer robots, is 
using medial axis retractation for clearance and a PRS (applied only on random DOF) 
which can address the problem of ~\ref{decoupled_DOF_optimization} but has longer 
computation time and is not using the information returned by the checker of which 
links are colliding to guide which DOF to choose for the PRS.

In some way, our method shares similarities with~\cite{PanSmoothSplineShort} 
since this latter method relies on collision checking and backtracks when an 
iteration is detected in collision, instead of trying to constantly satisfy 
distance constraints. Unlike our method however, the iterations are composed of 
Cubic-B-splines. The benefit of this method is that the result is a 
differentiable path.

@@

\begin{figure}[b]
	\centering
	\includegraphics[width=15cm]{contact-points.pdf}
	\caption{Constraint definition based on contact points.}
	\label{contact-points}
\end{figure}

@@

In the collision-configuration $\xx_{i+1}(\tcolli)$, let $\po_c\in \real^3$ be the 
contact point expressed in the global frame ${\cal R}_0$ of each of the two 
bodies. We compute (see Figure~\ref{contact-points}) the associated points $\po_1$ 
and $\po_2$ in the free-configuration $\xx_{i}(\tcolli)$, and the difference 
$\mathbf{u}=\po_2-\po_1$ which will be used as the orthogonal direction the bodies can not move along at the path parameter $\tcolli$.

Let $\translation^{*}\in \real^3$ denotes the position between frames of $\body_1$  
and $\body_2$ in configuration $\xx_i(\tcolli)$. Let $\translation \in 
\real^3$ (resp. $R\in SO(3)$) denote the same position (resp. rotation) in 
configuration $\xx (\tcolli)$ where $\xx$ is any path in $\CS^{wp}$.

We denote by $F$ the mapping from $\CS^{wp}$ to $\real^3$ defined by
\begin{equation}\label{eq:constraint}
F (\xx) =  R^T (\translation^{*} - \translation)
\end{equation}
Note that $F$ vanishes for any path $\xx$ such that in configuration
$\xx(\tcolli)$ the relative position of $\body_2$ w.r.t. $\body_1$ is equal to $
\translation^{*}$ or if the relative position $\translation^{*} - \translation$ is 
orthogonal to $\mathbf{u}$.

When a collision is detected at $\tcolli$ along path $\xx_{i+1}$, we wish to add
constraint
\begin{equation}\label{eq:non-linear constraint}
F (\xx) = 0
\end{equation}
However, as this constraint is non-linear, we linearize it around $\xx_i$:
$$
\frac{\partial F}{\partial \xx}(\xx_i)(\xx -\xx_i) = 0
$$
for any later iteration $\xx_j$, $j\geq i+1$.

@@

Let $q_{k\,i}$ denotes waypoint $k$ along path $x_i$.
The constraint on the position at $t_{coll\,i}$ is a function that depends only
on two waypoints $q_{k\,i}$, $q_{k+1\,i}$, with $0\leq k\leq n$. There exists 
$\beta\in[0,1]$ such that for any $j$:
$$
\xx_j (t_{coll\,i}) = (1-\beta) \conf_{k\,j} + \beta \conf_{k+1\,j}
$$
Therefore, the Jacobian $J_F$ of constraint~(\ref{eq:constraint}) with respect to 
$x$ is
$$
J_F = \left(\begin{array}{cccccc}
0 & \cdots & (1-\beta)\,\mathbf{u}^T \frac{\partial F}{\partial q} (\xx_j(t_{coll\,i})) & \
\beta\,\mathbf{u}^T \frac{\partial F}{\partial q} (\xx_j(t_{coll\,i})) & \cdots & 0
\end{array}
\right)
$$
Both $F$ and $\frac{\partial F}{\partial q}$ are provided by our path planning framework~\cite{hpp} as differentiable functions.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=7.5cm]{2d_final_green.png}
	%\noindent\rule{8cm}{0.8pt}
	\includegraphics[width=7.5cm]{concave_final_green.png}
	\caption{Path-optimization results on a 2D-ponctual robot, moving around 
	obstacles. Initial paths are in red, optimized ones in black. Grey paths 
	represent intermediate iterations, red dots colliding configurations and blue 
	dots the associated collision-free configurations of the backtracked paths 
	where constraints have been computed.}
	\label{2D_long}
\end{figure}

Figure~\ref{2D_long} shows several iterations of our optimizer on 2D cases. Since 
in this special case, transformation constraints are equivalent to compulsory 
configurations to pass through, we can verify that our optimized path is applying 
all computed constraints. We can also understand which collisions have led to 
the constraints.

@@

Figure~\ref{2D_long} illustrates a \textit{very long} path example that RS or PRS will not manage to 
optimize in an affordable time, because of probabilistically failing to sample 
configurations in the box. GB succeeds to optimize the 
path contained in the box, with the following cost coefficients 
$$
\lambda_{i-1} = \frac{1}{\sqrt{(\conf_{i\,0}-\conf_{i-1\,0})^T \weight^2 
(\conf_{i\,0}-\conf_{i-1\,0})}}
$$
aiming at keeping the same ratio between path segment lengths at 
minimum as at 
initial path, represented by the waypoints ($\conf_{i\,0})_{1\leq i\leq n+1}$.
Without these coefficients, the path that minimizes the cost corresponds to a 
straight line with the waypoints equidistantly allocated, which is not adapted for 
the Figure~\ref{local_box_optim} type of problems with a local passage very
constrained by obstacles. Note that this cost is also working with all other 
examples presented in this paper.

\begin{figure}[t]
	\centering
	\includegraphics[width=7.5cm]{local_box_optim.png}
	\caption{Case of a long initial path (above) containing a small part that can 
	be optimized (below). Random shortcut is unlikely to optimize the part containing detours in the box, whereas our method 
	succeeds (in blue).}
	\label{local_box_optim}
\end{figure}

@@

\begin{figure}[b]
	\centering
	\includegraphics[height=4.9cm,width=1.8cm]{pr2_initial_final_vertical.png}
	\includegraphics[width=5.7cm]{p0_pr2_alone_merged3.png}
	\includegraphics[height=4.9cm]{p1RS_pr2_alone_merged3.png}
	\includegraphics[height=4.9cm]{p1GB_pr2_alone_merged3.png}\\
	\caption{PR2-crossing-arms example. In this motion planning problem, PR2 robot 
	has just to 
exchange the positions of its arms. The task is simple, however, in absence of 
explicit indication, any probabilistic motion planner will compute a path that 
makes the PR2 mobile basis purposelessly moving. This is the case of RRT-connect 
algorithm (left). Path optimization is expected to remove unnecessary motions. 
The popular RS algorithm fails in this case (middle). Our GB algorithm 
succeeds (right).}
	\label{pr2_final}
\end{figure}

@@

@@

Optimization computation time and path length averages are presented for 30 runs of 
the PR2-crossing-arms in the Table~\ref{tab:results}. In the same way, time 
computation averages for the PR2-in-kitchen example have been 
calculated: $59.5\,\text{s}$ (GB) and $76.2\,\text{s}$ (RS).
Thus our method presents 
similar computation times and path lengths for mobile manipulation tasks. However, 
the extinction of the mobile base motion in the gradient-based optimized path is 
advanced in the right column of Table~\ref{tab:results}. Thus the problem addressed 
Figure~\ref{decoupled_DOF_optimization} is solved considering this DOF.

@@

\begin{table}
\centering
\scalebox{0.9}{
  \begin{tabular}{cccccc}
  \toprule
    \textbf{Problem} & Path obtained from & Computation time  & Path length & Cost & Base traveled distance\\
    \midrule
    \midrule
    & Initial &  & $14.3$ & $ $ &\\
    \textbf{Freeflyer-} & GB & $\,\text{ms}$ & $ $ & $ $ &\\
    \textbf{puzzle} & PRS & $6.53\,\text{ms}$ & $14.3$ & $ $ &\\
    & RS & $68.3\,\text{ms}$ & $6.05$ & $ $ &\\
    \midrule
    & Initial &  & $11.3$ & $ $ &\\
    \textbf{Double-arm} & GB & $318\,\text{ms}$ & $4.95$ & $ $ &\\
    \textbf{5-DOF} & PRS & $8.42\,\text{ms}$ & $8.73$ & $ $ &\\
    & RS & $61.9\,\text{ms}$ & $6.96$ & $ $ &\\
    \midrule
    & Initial &  & $10.8$ & $ $ & $8.03$\,\text{m}\\
    \textbf{PR2-crossing-} & GB & $24.8\,\text{s}$ & $1.90$ & $ $ & $10^{-7}\,\text{m}$\\
    \textbf{arms} & PRS & $41.1\,\text{s}$ & $ 4.73$ & $ $ & $0\,\text{m}$\\
    & RS & $31.5\,\text{s}$ & $1.60$ & $ $ & $2.70\,\text{m}$\\
    \midrule
    & Initial &  & $ $ & $ $ &\\
    \textbf{PR2-in-} & GB & $\,\text{s}$ & $ $ & $ $ &\\
    \textbf{kitchen} & PRS & $\,\text{s}$ & $ $ & $ $ &\\
    & RS & $\,\text{s}$ & $ $ & $ $ &\\
    \midrule
    & Initial &  & $ $ & $ $ &\\
    \textbf{6-DOF-arm-} & GB & $\,\text{s}$ & $ $ & $ $ &\\
    \textbf{with-spheres} & PRS & $\,\text{s}$ & $ $ & $ $ &\\
    & RS & $\,\text{s}$ & $ $ & $ $ &\\
    \midrule
    & Initial &  & $ $ & $ $ &\\
    \textbf{6-DOF-arm-} & GB & $\,\text{s}$ & $ $ & $ $ &\\
    \textbf{through-window} & PRS & $\,\text{s}$ & $  $ & $ $ &\\
    & RS &  $\,\text{s}$ & $ $ & $ $ &\\
    \midrule
    & Initial &  & $19.0$ & $ $ &\\
    \textbf{Baxter-in-} & GB & $2449\,\text{s}$ & $5.85$ & $ $ &\\
    \textbf{office} & PRS & $638\,\text{s}$ & $17.5$ & $ $ &\\
    & RS & $139\,\text{s}$ & $13.3$ & $ $ &\\
    \bottomrule
  \end{tabular}
  }%scalebox
\caption{Average results for 30 runs of several examples presented in the paper or 
the video. For each run, a solution path is planned by Visibility-PRM as initial 
guess for each optimizer. $\alpha_{init}$ is set to 0.1.
For the PR2-crossing-arms example only, the right column represents the 
distance that is traveled by the robot mobile base during the different paths.
}
\label{tab:results}
\end{table}

>>>>

\jvol{00} \jnum{00} \jyear{2015} \jmonth{October}

@@

For this shortening purpose, random shortcut (RS) methods are
still very 
popular~\cite{Sekhavat-Svestka1998,Geraerts04clearancebased,HauserFastSmooth}. 
However, RS requires fine 
tuning of the termination condition (see 
Algorithm~\ref{algo:random-shortcut}) and is no efficient due to randomness for long 
trajectories where only a small part needs to be optimized. 
Figure~\ref{decoupled_DOF_optimization} presents another situation where RS will 
always fail to optimize the initial path, since it cannot decouple the 
robot degrees of freedom (DOF) on which the optimization occurs, contrary to our 
algorithm or partial random shortcut (PRS) methods~\cite{Geraerts04clearancebased} 
that shortcut only one or a group of DOF.

@@

The idea of our method is to find a good trade-off between
the simplicity of “blind” methods like shortcut algorithm,
and the complexity of distance based optimization techniques.
The method iteratively shortens the initial path with gradient-based information.
When a collision is detected at a given iteration, the method backtracks to the
latest valid iteration and inserts a one-dimensional constraint
between the objects detected in collision. Only collisions between objects are 
evaluated, therefore no pre-processing of the
robot or environment models is necessary to increase distance computation speed. 
Preserving the problem geometry also 
guarantees that a solution can still be found, e.g. for narrow passages as holes or 
grippers. The underlying optimization algorithm is a quadratic program.

@@

Some heuristics use random shortcuts on the initial guess combined with a 
trajectory re-building that returns ${C}^1$ shortcuts made of parabolas and lines 
(bang-bang control)~\cite{HauserFastSmooth}. These local refined trajectories 
are time-optimal since they comply with acceleration and velocity constraints. 
~\cite{Guernane2011}, also based on random shooting, is guiding configuration-
generation with local holonimic considerations. But this method remains only locally 
optimal, and is not addressing high-DOF problems.
~\cite{Geraerts04clearancebased}, whereas just implemented for freeflyer robots, is 
using medial axis retractation for clearance and a PRS (applied only on random DOF) 
which can address the problem of Figure~\ref{decoupled_DOF_optimization} but is 
relatively slower than RS. Moreover, PRS is not using the information returned by 
the checker of which links are colliding to guide which DOF or group of DOF are 
relevant to shortcut, contrary to our method.

In some way, our method shares similarities with~\cite{PanSmoothSplineShort} 
since this latter method relies on collision checking and backtracks when an 
iteration is detected in collision, instead of trying to constantly satisfy 
distance constraints. Unlike our method however, interpolating configuration -which 
can be viewed as constraints- are freezing the whole robot configuration instead of 
a relevant subpart. Thus, this method cannot solve the 
Figure~\ref{decoupled_DOF_optimization} problem.

%Unlike our method however, the iterations are composed of 
%Cubic-B-splines. The benefit of this method is that the result is a 
%differentiable path.

@@

\begin{figure}[b]
	\centering
	\includegraphics[width=15cm]{contact-points.pdf}
	\caption{Bodies representation in collision-configuration (left) and 
	backtracked free-configuration (right). A contact point (i.e. any point in 
	the intersection of the bodies) $\po_c$ can be returned by the Flexible 
	Collision Library~\cite{fcl}, used to detect collisions. The red $(\perp)$ 
	line is orthogonal to ($\po_2$,$\mathbf{u}$) and represents the motion 
	direction which is allowed by the constraint.}
	\label{contact-points}
\end{figure}

@@

In the collision-configuration $\xx_{i+1}(\tcolli)$, let $\po_c\in \real^3$ be a 
contact point expressed in the global frame ${\cal R}_0$ of each of the two 
bodies (Figure~\ref{contact-points} left). We compute the associated points $\po_1$ 
and $\po_2$ in the free-configuration $\xx_{i}(\tcolli)$, and the difference 
$\mathbf{u}=\po_2-\po_1$ which will be used as the orthogonal direction the 
bodies can not move along at the path parameter $\tcolli$ 
(Figure~\ref{contact-points} right).

%Let $\translation^{*}\in \real^3$ denotes the position between frames of $
%\body_1$  and $\body_2$ in configuration $\xx_i(\tcolli)$. Let $\translation \in 
%\real^3$ (resp. $R\in SO(3)$) denote the same position (resp. rotation) in 
%configuration $\xx (\tcolli)$ where $\xx$ is any path in $\CS^{wp}$.

Let $M^{*}\in SE(3)$ denote the homogeneous transformation between frames of $
\body_1$  and $\body_2$ in configuration 
$\x_i(\tcolli)$. Let $M\in SE(3)$ denote the same transformation in configuration 
$\x (\tcolli)$ where $\x$ is any path 
in $\CS^{wp}$. Let $R\in SO(3)$ and $\translation\in\real^3$ 
(resp. $\translation^{*}$) be the rotation 
and translation parts of $M$ (resp. $M^{*}$).

We denote by $F$ the path constraint defined by the mapping from $\CS^{wp}$ to $
\real^3$ defined by
\begin{equation}\label{eq:constraint}
F (\xx) =  \mathbf{u}^T R^T (\translation^{*} - \translation)
\end{equation}
where the product $R^T (\translation^{*} - \translation)$ is used to express the translations difference in the global frame ${\cal R}_0$.

Note that $F$ vanishes for any path $\xx$ such that in configuration
$\xx(\tcolli)$ the relative position of $\body_2$ w.r.t. $\body_1$ is equal to $
\translation^{*}$ or if the relative position $\translation^{*} - \translation$ is orthogonal to $\mathbf{u}$.

When a collision is detected at $\tcolli$ along path $\xx_{i+1}$, we wish to add
constraint
\begin{equation}\label{eq:non-linear constraint}
F (\xx) = 0
\end{equation}
However, as this constraint is non-linear, we linearize it around $\xx_i$:
$$
\frac{\partial F}{\partial \xx}(\xx_i)(\xx -\xx_i) = 0
$$
for any later iteration $\xx_j$, $j\geq i+1$. Both $F$ and $\frac{\partial F}{\partial \conf}$ are provided by our path planning framework~\cite{hpp} as differentiable functions.

@@

Let $q_{k\,i}$ denote the waypoint $k$ along path $x_i$.
The constraint on the position at $t_{coll\,i}$ is a function that depends only
on two waypoints $q_{k\,i}$, $q_{k+1\,i}$, with $0\leq k\leq n$. There exists 
$\beta\in[0,1]$ such that for any $j$:
$$
\xx_j (t_{coll\,i}) = \conf_{k\,j} + \beta (\conf_{k+1\,j} - \conf_{k\,j})
$$
The path Jacobian $J_F$ of constraint~(\ref{eq:constraint}) w.r.t. $x$ is thus built by block using the previous constraint jacobian $\frac{\partial F}{\partial \conf}$ and $\beta$. ????
%Therefore, the Jacobian $J_F$ of constraint~(\ref{eq:constraint}) with respect to 
%$x$ is
%$$
%J_F = \left(\begin{array}{cccccc}
%0 & \cdots & (1-\beta)\,\mathbf{u}^T \frac{\partial F}{\partial q} (\xx_j(t_{coll\,i})) & \
%\beta\,\mathbf{u}^T \frac{\partial F}{\partial q} (\xx_j(t_{coll\,i})) & \cdots & 0
%\end{array}
%\right)
%$$

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=7.8cm]{contact_points6.png}
	%\noindent\rule{8cm}{0.8pt}
	\includegraphics[width=8cm]{contact_points2potential.png}
	\caption{Path-optimization results on 2D-ponctual robots, moving around 
	green obstacles. Initial paths are in red, optimized ones in black. Grey paths 
	represent intermediate iterations, red and black dots resp. $\po_1$ and $\po_2$ 
	points, red segments $\mathbf{u}$ and blue circles collision-free configurations 
	of the backtracked paths 
	where constraints have been computed.}
	\label{2D_long}
\end{figure}

Figure~\ref{2D_long} shows several iterations of our optimizer on 2D cases. Since 
in this special case, orthogonal constraints are equivalent to forbidden motion 
direction, we can verify that our optimized path is applying 
all computed constraints. We can also understand which collisions have led to 
the constraints.

@@

Figure~\ref{local_box_optim} illustrates a \textit{very long} path example that RS or PRS will not manage to 
optimize in an affordable time, because of probabilistically failing to sample 
configurations in the box. GB succeeds to optimize the 
path contained in the box, with the following cost coefficients 
$$
\lambda_{i-1} = \frac{1}{\sqrt{(\conf_{i\,0}-\conf_{i-1\,0})^T \weight^2 
(\conf_{i\,0}-\conf_{i-1\,0})}}
$$
aiming at keeping the same ratio between path segment lengths at 
minimum as at 
initial path, represented by the waypoints ($\conf_{i\,0})_{1\leq i\leq n+1}$.
Without these coefficients, the path that minimizes the cost corresponds to a 
straight line with the waypoints equidistantly allocated, which is not adapted for 
the Figure~\ref{local_box_optim} type of problems with a local passage very
constrained by obstacles. Note that this cost is also working with all other 
examples presented in this paper.

\begin{figure}[t]
	\centering
	\includegraphics[width=7.5cm]{local_box_optim.png}
	\caption{Case of a long initial path (above) containing a small part that can 
	be optimized (below). Random shortcut is unlikely to optimize the part 
	containing detours in the box, whereas our method 
	succeeds (in blue). This type of issue is common in navigation problems in 
	environments with long corridors.}
	\label{local_box_optim}
\end{figure}

@@

\begin{figure}[b]
	\centering
	\includegraphics[height=4.9cm,width=1.8cm]{pr2_initial_final_vertical.png}
	\includegraphics[width=5.7cm]{p0_pr2_alone_merged3.png}
	\includegraphics[height=4.9cm]{p1RS_pr2_alone_merged3.png}
	\includegraphics[height=4.9cm]{p1GB_pr2_alone_merged3.png}\\
	\caption{PR2-crossing-arms example. In this motion planning problem, PR2 robot 
	has just to 
exchange the positions of its arms. The task is simple, however, in absence of 
explicit indication, any probabilistic motion planner will compute a path that 
makes the PR2 mobile base purposelessly moving. This is the case of RRT-connect 
algorithm (left). Path optimization is expected to remove unnecessary motions. 
The popular RS algorithm fails in this case (middle). Our GB algorithm 
succeeds (right).}
	\label{pr2_final}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=6cm]{fiad_qinit.png}
	\includegraphics[width=6cm]{fiad_qfinal.png}\\
	\includegraphics[width=6cm]{fiad_real.png}
	\includegraphics[width=6cm]{fiad-trajectorires.png}

	\caption{(Bottom left) An industrial use-case example proposed by Philips for 	
	the 
	Factory-in-a-Day project~\cite{factory-day-video}. A similar environment have 
	been created (top) to 
	illustrate that our method can comply with an industrial problem, where 
	initial and final configurations are constrained in boxes. Trajectories results 
	are presented (bottom right).}
	\label{fiad}
\end{figure}

@@

Optimization computation time and path length averages are presented for 30 runs of 
the PR2-crossing-arms in the Table~\ref{tab:results}. In the same way, time 
computation averages for the PR2-in-kitchen example have been 
calculated: $59.5\,\text{s}$ (GB) and $76.2\,\text{s}$ (RS).
Thus our method presents 
similar computation times and path lengths for mobile manipulation tasks. However, 
the disappearance of the mobile base motion in the gradient-based optimized path is 
shown in the right column of Table~\ref{tab:results}. Thus the problem addressed 
Figure~\ref{decoupled_DOF_optimization} is solved considering this DOF.

@@

\begin{table}
\centering
\scalebox{0.9}{
  \begin{tabular}{cccccc}
  \toprule
    \textbf{Problem} & Path obtained from & Computation time  & Path length & Cost & Base traveled distance\\
    \midrule
    \midrule
    & Initial &  & $14.3$ & $ $ &\\
    \textbf{Freeflyer-} & GB & $\,\text{ms}$ & $ $ & $ $ &\\
    \textbf{puzzle} & PRS & $6.53\,\text{ms}$ & $14.3$ & $ $ &\\
    & RS & $68.3\,\text{ms}$ & $6.05$ & $ $ &\\
    \midrule
    & Initial &  & $11.3$ & $ $ &\\
    \textbf{Double-arm} & GB & $318\,\text{ms}$ & $4.95$ & $ $ &\\
    \textbf{5-DOF} & PRS & $8.42\,\text{ms}$ & $8.73$ & $ $ &\\
    & RS & $61.9\,\text{ms}$ & $6.96$ & $ $ &\\
    \midrule
    & Initial &  & $10.8$ & $ $ & $8.03$\,\text{m}\\
    \textbf{PR2-crossing-} & GB & $24.8\,\text{s}$ & $1.90$ & $ $ & $10^{-7}\,\text{m}$\\
    \textbf{arms} & PRS & $41.1\,\text{s}$ & $ 4.73$ & $ $ & $0\,\text{m}$\\
    & RS & $31.5\,\text{s}$ & $1.60$ & $ $ & $2.70\,\text{m}$\\
    \midrule
    & Initial &  & $15.0$ & $ $ &\\
    \textbf{PR2-in-} & GB & $288\,\text{s}$ & $4.40$ & $ $ &\\
    \textbf{kitchen} & PRS & $431\,\text{s}$ & $12.1$ & $ $ &\\
    & RS & $95.6\,\text{s}$ & $5.33$ & $ $ &\\
    \midrule
    & Initial &  & $ $ & $ $ &\\
    \textbf{6-DOF-arm-} & GB & $\,\text{s}$ & $ $ & $ $ &\\
    \textbf{with-spheres} & PRS & $\,\text{s}$ & $ $ & $ $ &\\
    & RS & $\,\text{s}$ & $ $ & $ $ &\\
    \midrule
    & Initial &  & $ $ & $ $ &\\
    \textbf{6-DOF-arm-} & GB & $\,\text{s}$ & $ $ & $ $ &\\
    \textbf{through-window} & PRS & $\,\text{s}$ & $  $ & $ $ &\\
    & RS &  $\,\text{s}$ & $ $ & $ $ &\\
    \midrule
    & Initial &  & $19.0$ & $ $ &\\
    \textbf{Baxter-in-} & GB & $2449\,\text{s}$ & $5.85$ & $ $ &\\
    \textbf{office} & PRS & $638\,\text{s}$ & $17.5$ & $ $ &\\
    & RS & $139\,\text{s}$ & $13.3$ & $ $ &\\
    \bottomrule
  \end{tabular}
  }%scalebox
\caption{Average results for 30 runs of several examples presented in the paper or 
the video. For each run, a solution path is planned by Visibility-PRM as initial 
guess for each optimizer. $\alpha_{init}$ is set to 0.1.
For the PR2-crossing-arms example only, the right column represents the 
distance that is traveled by the robot mobile base during the different paths.
}
\label{tab:results}
\end{table}
